% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jianli.li}

\basicInfo{
  \email{alexan.lee@pku.edu.cn} \textperiodcentered\ 
  \phone{(+86) 189-119-63820} \textperiodcentered\ 
  \linkedin[Jianli.li]{http://www.linkedin.com/in/alexan-见黎-lee-李-a9627257/}} 

\section{\faUsers\ Work Experience}

\datedsubsection{\textbf{DiDi} ，Beijing}{December 2020 - Present}
\
\role{Recommendation algorithm}{Senior Algorithm Engineer}
\begin{onehalfspacing}
Main tasks: Responsible for recommending the main ranking model and image-related algorithms.
\begin{itemize}
\item The model building and automation of small and medium-sized cities has increased the conversion rate by 2.0PP, saving 2 person-days per city.
\item The main ranking model is iterated, adding features such as images and hours and optimizing the model, the offline AUC is increased by 0.5+PP, and the online conversion rate is increased by 0.24PP.
\item Dishes image review.
\end{itemize}
\end{onehalfspacing}

\datedsubsection{\textbf{DeepZero（Ipinyou）} ，Beijing}{July 2019 - November 2020}
\role{Algorithm Platform}{Head of Intelligent Decision Algorithm Group, 9 subordinates}
\begin{onehalfspacing}
Main tasks: Responsible for the construction of intelligent decision-making algorithm platform.
\begin{itemize}
\item  Responsible for the company's intelligent decision algorithm platform construction and product output, completed the construction of the Leads Scoring machine learning platform of a large car company, and the construction of a large pharmaceutical company's influenza prediction machine learning platform, etc., and gradually precipitated and led the company's Holmes product research and development.
\end{itemize}
\end{onehalfspacing}

\role{CTR, CVR estimation}{Brand and performance advertising algorithm group leader, 4 subordinates}
\begin{onehalfspacing}
Main tasks: fully responsible for the company's brand and performance advertising algorithms.
\begin{itemize}
\item The consumption and ROI of a certain top e-commerce, luxury e-commerce, and travel customers in the company have been greatly improved year-on-year and month-on-month. The full-link solution to the performace of the problem has doubled the cost of an e-commerce company and doubled the ROI .
\item With the launch of more than 20+ brand advertising projects of service companies, the TA concentration has been comprehensively improved and guaranteed.
\end{itemize}
\end{onehalfspacing}

\datedsubsection{\textbf{Ipinyou} ，Beijing}{July 2018 - July 2019}
\role{CTR, CVR estimation}{Advertising algorithm engineer, head of brand algorithm group, 1 subordinate}
\begin{onehalfspacing}
Main tasks: Responsible for the research and practice of computational advertising related algorithms such as CVR estimation, intelligent traffic distribution, and target population training.
\begin{itemize}
\item The TA concentration algorithm is realized, and the company's TA service system from 0 to 1 is built, so that the accuracy of the algorithm TA reaches 78\%+. 
\item The construction of the CVR estimation data stream shortens the training time by more than 5 hours on average.
\item Improve the feature system, add 9 basic features, and use FFM, MLR and other model methods to fit non-linear features, and the offline AUC will increase by about 5\% on average.
\item Using the customer unit price to build an ROI model, both online ROI and customer unit price have increased significantly.
\item Design and implementation of PDB traffic distribution algorithm.
\item Exploration and implementation of ESMM global conversion rate estimation model in DSP advertising system.
\end{itemize}
\end{onehalfspacing}

\datedsubsection{\textbf{Cheetah Mobile} ，Beijing}{March 2016 - July 2018}
\role{CTR, CVR estimation}{Advertising algorithm}
\begin{onehalfspacing}
Main tasks: Maintenance of Cheetah Mobile's advertising monetization algorithm, hourly level transformation of advertising model, PC model construction, participation in Cheetah Mobile hackathon model group competition, etc.
\begin{itemize}
  \item Take over and maintain the previous model data flow, switch clusters, etc., ensure the stable operation of the original model, and reorganize each data flow and relationship in detail during the switching process, making the data flow clearer and more maintainable.
  \item CTR model hour-level transformation. The successful completion of the transformation increased the click-through rate by about 5\%.
  \item The PC model was built. Faced with the difficulties of large display of PC business, small click volume, and very sparse data, the down-sampling method was used to reduce the display volume, and the experiment finally achieved the effect of increasing revenue by 5\% to 10\%.
  \item Actively participated in the Cheetah Hackathon model group, predicted Twitter expressions based on the text, and achieved good results.
  \item Obtained a patent related to traffic monitoring, using threshold method, proportional method, and Deep \& Wide method for traffic monitoring. See：http://dbpub.cnki.net/grid2008/Dbpub/detail.aspx?dbname=SCPD\&filename=CN107124320A
  \item App data analysis, detailed inventory of advertising data and other data and user behavior relationship.     
\end{itemize}
\end{onehalfspacing}


\role{Traffic management platform}{Back-end R\&D, project leader, 2 subordinates}
\begin{onehalfspacing}
Main work: Cheetah Mobile’s advertising traffic management platform (SSP), as the company’s unified traffic management platform, needs to take into account the needs and services of multiple parties (CFP, ADX, CSS, S2S, SDK, etc.), and it needs to face many people including traffic parties, Operations, finance, data, etc., effectively support the development of the company's monetization business, integrate company traffic, support the management of 1,000+ traffic parties, and 30,000+ advertising spaces. In 2017, the affiliate advertising business increased by about 700\%. See:publishers.cmcm.com，manager.peg.cmcm.com
\begin{itemize}
  \item Participate in the overall planning and design of the system. The system is based on Spring MVC, Shiro, Mybatis, MySQL, Druid, Active MQ and other technical systems.
  \item The background development of the entire system. Development of core functions such as advertising space management, traffic monitoring, offer list, API data service, etc., self-developed authority system: including function authority and data authority.
  \item The development of report functions uses design patterns such as factory methods, and is compatible with multiple data sources and multiple style output report services.
  \item Development of timed tasks and interactive services with other systems.
  \item Use Git as a project management tool and Jenkins as a build tool to realize one-click automatic online deployment.
  \item System service transformation, based on Spring Cloud for service transformation. 
\end{itemize}
\end{onehalfspacing}

\datedsubsection{\textbf{Neusoft Group Co., Ltd.}}{July 2012 - October 2015}
\role{Financial Software and Infrastructure Software Platform of the State Administration of Taxation}{Core R\&D，2015}
\begin{onehalfspacing}
Work content: part of the maintenance of the financial software of the State Administration of Taxation, as well as different types of customized development work, maintenance of infrastructure software, and customized development work.
\begin{itemize}
  \item Work challenges: complex communication, high data quality requirements, complex business logic, and wide application scope.
  \item Main technical architecture: Spring, weblogic, oracle, IBM MQ, linux architecture.
\end{itemize}
\end{onehalfspacing}

\role{Gansu Provincial Land Tax Data Analysis Platform}{Core R\&D，2014}
\begin{onehalfspacing}
Work content: Build a unified data analysis platform for diversified tax-related data, including core collection and management, construction and installation, invoice information, audit law, and financial data.
\begin{itemize}
  \item Participate in the overall design of the platform, complete the design, development, and maintenance of the tax risk module, and participate in the design and development of 10+ multi-dimensional statements in the later period.
  \item Main challenges: diversified data sources, large amount of data and large increments, complex business logic, and diverse communication.
  \item Main technical architecture, JSP, Struts, Spring, SAP, Oracle, data stage, linux, weblogic, etc.
  \item Among them, the feature extraction of indicators is performed, and machine learning methods such as clustering and decision trees are used.
  \item The project won the Provincial Excellent Information Software Award.
\end{itemize}
\end{onehalfspacing}

\role{Qingdao Local Taxation Risk Management System}{Core R\&D，2013}
\begin{onehalfspacing}
Work content: Develop the monitoring and evaluation of the city's tax collection and management data under different risk indicator calculation models, and push and feedback to taxpayers and tax officials, and be responsible for the identification of hundreds of thousands of taxpayers with an average of over one million tax information per month And processing.
\begin{itemize}
  \item Taxation has the characteristics of complex business logic, large amount of data, multiple indicators, strict data requirements, and timeliness.
  \item Using JSP, Struts, Spring, DRM (internal data processing framework), weblogic, Oracle, Linux/Aix/Solaris architecture, design and development of multi-threaded, distributed computing task execution framework.
  \item The calculation indicators mainly adopt the threshold method, Chebyshev method and other calculation models.
  \item Successful completion of all stages of delivery.
\end{itemize}
\end{onehalfspacing}


\section{\faGraduationCap\  Education background}
\datedsubsection{\textbf{Tsinghua University}, Beijing}{2020.09 -- 2023.06}
\textit{Master degree，Unified recruitment part-time}\ Engineering Management.
 Main courses: strategic management, managerial economics, systems engineering, systems engineering and optimization, etc.
 
\datedsubsection{\textbf{Peking University}, Beijing}{2016.02 -- 2019.06}
\textit{Master degree，Unified recruitment part-time}\ Software engineering.
 Main courses: software architecture and design, algorithm design and analysis, cloud computing technology and application, advanced object-oriented technology courses, software engineering process and project management, etc.
 
\datedsubsection{\textbf{He Bei University}, Hebei}{2008.09 -- 2012.06}
\textit{Bachelor's degree，Unified recruitment full-time}\ Information and Computing Science.
 Main courses: Mathematical Analysis, Advanced Algebra, Data Structure, Operating System, Principle of Computer Composition, Computer Network, Principle of Microcomputer and Interface Technology, etc.


\section{\faCogs\ IT skills}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item Programming languages: Java, Python, SQL, Scala, C++, Shell, etc.
  \item Platform: mac, Linux.
  \item Software designer, management number：141562003。
  \item Passed Alibaba programming specification certification, certificate number：CLDT02180700030807。
 \item Aliyun artificial intelligence engineer certification, certificate number：ACA05210400230527L。
  \item Five patents:
[1]Li Jianli. Monitoring method, device and server of traffic data[P]. Beijing：CN107124320A,2017-09-01.

[2]Li Jianli. Advertisement data processing method and device[P]. Beijing：CN110033314A,2019-07-19.

[3]Li Jianli. Method and device for determining the concentration of target audience[P]. Beijing：CN110222750A,2019-09-10.

[4]Li Jianli. Crowd division method and device[P]. Beijing：CN111563775A,2020-08-21.

[5]Li Jianli. Data processing method and device[P]. Beijing：CN112085528A,2020-12-15.
\end{itemize}

\section{\faHeartO\ Awards}
\datedline{Didi Chuxing First Quarter Project Excellent Team Award}{2021}
\datedline{Excellent Team Award for an Effect Project of Pinyou}{2019}
\datedline{Pinyou's 2018 Shining Star}{2019}
\datedline{Excellent Team Award for a Brand Project of Pinyou}{2018}
\datedline{\textit{87/468 people}, AI Challenger Global Challenge Fine-grained User Comment Sentiment Analysis}{October 2018}
\datedline{\textit{265/5204 people}, Tianchi advertising conversion rate prediction contest}{May 2018}
\datedline{\textit{426/3152 people}, Meinian Health AI Competition-Double High Disease Risk Prediction}{June 2018}
\datedline{\textit{4/7th}, Cheetah Mobile Hackathon}{May 2017}
\datedline{Cheetah Mobile OAT2017 Outstanding Contribution Award}{2017}
\datedline{Team Excellence Award}{2017}
\datedline{Provincial Excellent Information Software Award}{2014}

\section{\faInfo\ other}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/AlexanLee
  \item Know the column: https://zhuanlan.zhihu.com/c\_1078664876162854912
  \item Language: English-proficient, barrier-free communication with overseas colleagues and customers to solve problems.
  \item Hobbies: Adhere to swimming once a week, and also like team activities. He won the runner-up of the Cheetah Mobile Macau City Orienteering Team.
 \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
